% ft-08a-LogExpoWorkSheet.tex
% Dropbox for Excel Project A
% Due date: Monday, November 7, at 11:59pm. Late submissions attract penalties.

\documentclass[11pt]{article}
\usepackage{enumerate}
\usepackage{syllogism} 
\usepackage{october}
\usepackage[table]{xcolor}

\begin{document}

\textbf{Work Sheet Term Test B Preparation}

1. Solve the following equations. Remember that $\log$ is the common
logarithm $\log_{10}$. 

\begin{equation}
  \label{eq:vibeibie}
3^{x}=\frac{1}{81}
\end{equation}
\begin{equation}
  \label{eq:gofushoo}
\pi^{x}=15
\end{equation}
\begin{equation}
  \label{eq:aepheipi}
e^{-x}=17.54
\end{equation}
\begin{equation}
  \label{eq:ohwoojie}
15.6^{x+2}=23^{x}
\end{equation}
\begin{equation}
  \label{eq:vogeobab}
\log{}x^{2}=(\log{}x)^{2}
\end{equation}
\begin{equation}
  \label{eq:mahbeizo}
2\log_{2}3-\log_{2}x=\log_{2}45
\end{equation}
\begin{equation}
  \label{eq:chohtohk}
x^{\log{}x}=1000x^{2}
\end{equation}
\begin{equation}
  \label{eq:ohdiedoe}
\ln{}x-\ln\frac{1}{3}=1
\end{equation}
\begin{equation}
  \label{eq:pohkaith}
\ln(2x-1)-2\ln{}4=3\ln{}2
\end{equation}
\begin{equation}
  \label{eq:aejaiquo}
5^{x+2}=e^{2x}
\end{equation}
\begin{equation}
  \label{eq:yohlaehu}
e^{x}+e^{-x}=3
\end{equation}
Hint for (\ref{eq:yohlaehu}): multiply by $e^{x}$ and solve quadratic
equation in $e^{x}$.

2. Solve the following word problems.

(a) Oil is heated to 60$^{\circ}C$. It cools to 50$^{\circ}C$ after 6
minutes. Find the time taken by the oil to cool from 50$^{\circ}C$ to
40$^{\circ}C$ (surrounding temperature $T=25^{\circ}C$).

(b) The distance $x$ traveled by a motorboat $t$ seconds after the
engine is cut off is given by $x=k^{-1}\ln(kv_{0}t+1)$, where $v_{0}$
is the velocity of the boat at the time the engine is cut and $k$ is a
constant. Find how long it takes a boat to go 150 metres when
$v_{0}=12.0$m/s and $k=6.80\cdot{}10^{-3}$ per metre.

(c) A pot of soup starts at a temperature of 373K, and the
surrounding temperature is 293K. If the cooling constant is
$k=-0.00150$ per seconds, what will the temperature of the pot of soup
be after twenty minutes (in Celsius)? (K stands for Kelvin, the formula
is $^{\circ}C$=K-273.15.)

(d) A rod of iron is heated in a forge to a temperature of 1280K.
The rod is then plunged into a bucket of chilled water with a
temperature of 280K. After ten seconds, the temperature of the iron
rod drops to 329.7K. What was the temperature of the iron after five
seconds?

(e) As part of his summer job at a restaurant, Jim learned to cook up
a big pot of soup late at night, just before closing time, so that
there would be plenty of soup to feed customers the next day. He also
found out that, while refrigeration was essential to preserve the soup
overnight, the soup was too hot to be put directly into the fridge
when it was ready. The soup had just boiled at 100$^{\circ}C$, and the
fridge was not powerful enough to accomodate a big pot of soup if it
was any warmer than 20$^{\circ}C$. Jim discovered that by cooling the
pot in a sink full of cold water (kept running, so that its
temperature was roughly constant at 5$^{\circ}C$) and stirring
occasionally, he could bring the temperature of the soup to
60$^{\circ}C$ in ten minutes. How long before closing time should the
soup be ready so that Jim could put it in the fridge and leave on
time?

(3) Evaluate the following limits.

\begin{equation}
  \label{eq:pheighou}
\lim_{x\rightarrow{}4}\sqrt{x^{2}-7}
\end{equation}
\begin{equation}
  \label{eq:yoozeice}
\lim_{x\rightarrow{}3}\frac{x^{2}-2x-3}{3-x}
\end{equation}
\begin{equation}
  \label{eq:eiteuyoe}
\lim_{x\rightarrow{}1/3}\frac{3x-1}{3x^{2}+5x-2}
\end{equation}
\begin{equation}
  \label{eq:igeeraos}
\lim_{x\rightarrow\infty}\frac{3x^{2}+4.5}{x^{2}-1.5}
\end{equation}
\begin{equation}
  \label{eq:laideico}
\lim_{x\rightarrow\infty}\frac{1-2x^{2}}{(4x+3)^{2}}
\end{equation}
\begin{equation}
  \label{eq:ikoebuba}
\lim_{x\rightarrow\infty}\frac{\frac{1}{3}x^{2}-\pi{}x+\frac{3}{4}}{\frac{3}{7}x^{2}+9x-\frac{1}{14}}
\end{equation}

\end{document}

