% ft-excel-project.tex
% Dropbox for Excel Project A
% Due date: Monday, November 7, at 11:59pm. Late submissions attract penalties.

\documentclass[11pt]{article}
\usepackage{enumerate}
\usepackage{syllogism} 
\usepackage{october}
\usepackage[table]{xcolor}

\begin{document}

\textbf{Excel Term Projects}

Due date: Monday, November 27, at 11:59pm. Late submissions attract
penalties.

Do not open the \texttt{csv} files directly from your browser by
left-clicking on it. Download it to your computer first (by
right-clicking) and then open it from MS Excel. Locations of source
files:

\texttt{http://www.streetgreek.com/lpublic/math1441/excel-project-A/}

\texttt{http://www.streetgreek.com/lpublic/math1441/excel-project-B/}

\textbf{Project A}

Open the file \texttt{A01010077-pone.csv}, where \texttt{A01010077} is
\emph{your} student number. Enter the following in your address bar
(replacing \texttt{A01010077} by your own student number):

\begin{quote}
  \texttt{http://www.streetgreek.com/lpublic/math1441/excel-project-A/A01010077-pone.csv}
\end{quote}

Save the \texttt{csv} file as a \texttt{xlsx} file, leaving the name
as is.

A company has a sales team of ten people in Africa. The file reflects
their sales numbers (in Canadian dollars) per country.

\begin{enumerate}
\item Create a column and insert a formula counting the number of countries
where the respective agent is active. Where the agent is not active in
a country, the cell is empty.
\item Create another column and insert a formula showing the total sales of
  each agent (sum the dollar amounts).
\item Sort the spreadsheet by total sales amount for all of Africa,
  putting the agent with the highest sales number first.
\item Create a row and insert a formula showing how many sales agents
  make sales worth more than \$30,000 for each country. Put the
  maximum of all these numbers in cell A13, using a formula. Put the
  name of the corresponding country in cell A14.
\end{enumerate}

Save the file and submit it in the appropriate dropbox. Project B is
on the next page.

\newpage

\textbf{Project B}

Open the file \texttt{A01010077-ptwo.csv}, where \texttt{A01010077} is
\emph{your} student number. Enter the following in your address bar
(replacing \texttt{A01010077} by your own student number):

\begin{quote}
  \texttt{http://www.streetgreek.com/lpublic/math1441/excel-project-A/A01010077-ptwo.csv}
\end{quote}

Save the \texttt{csv} file as a \texttt{xlsx} file, leaving the name
as is.

A physicist takes measurements of a distance (in millimetres) after a
certain amount of time (in seconds). She records the result in a
\texttt{csv} file. After looking at the scatter plot, she is fairly
sure that there is a linear relationship with time as an independent
variable and distance as a dependent variable.

\begin{enumerate}
\item Sort the data by time in ascending order.
\item Insert a scatter plot.
\item Insert a linear trendline and display the equation on the chart.
\item Below the data, record the following three times: 25, 45, and 60
  (seconds). Do this in cells A23, A24, and A25. Then, record
  the projected distance for these times as a formula in B23, B24, and
  B25.
\end{enumerate}

Save the file and submit it in the appropriate dropbox.

\end{document}

