% ft-lab-02.tex

\documentclass[11pt]{article}
\usepackage{enumerate}
\usepackage{syllogism} 
\usepackage{october}
\usepackage[table]{xcolor}

\newcounter{aufg}
\setcounter{aufg}{0}
\newcommand{\aufgabe}[0]{\refstepcounter{aufg}\textbf{(\arabic{aufg})}}

\begin{document}

\textbf{Quadratic Equations, Mixtures, and Percent}

{\aufgabe} An American city is divided into two voting districts. One
is predominantly Republican (voting population 260,000, 61\% vote
Republican); the other votes predominantly for the Democratic Party
(voting population 170,000, 47\% vote Republican). You want to
gerrymander the districts so that both of them will predominantly vote
Republican. How many voting people in the larger district do you have
to move to the smaller district to get 51\% Republicans in the smaller
district?

{\aufgabe} Solve the following quadratic equations:
\begin{equation}
  \label{eq:ahzeiphe}
  0.09x^{2}=289
\end{equation}
\begin{equation}
  \label{eq:egohleyo}
  (2+3x)^{2}=(3+x)(5x-3)+13
\end{equation}
\begin{equation}
  \label{eq:goobahch}
  \frac{3x-10}{x-2}-\frac{x-4}{x+1}=1
\end{equation}

{\aufgabe} The product of two consecutive negative integers is 1122. What are
the numbers?

{\aufgabe} A garden measuring 12 meters by 16 meters is to have a pedestrian
pathway installed all around it, increasing the total area to 285
square meters. What will be the width of the pathway? See diagram.

{\aufgabe} A fast train runs 8 mi/h faster than a slow train and takes 3 hours
less to travel 288 miles. Find the rates of the trains.

{\aufgabe} The length of a rectangle court exceeds its width by 2 metres. If the
length and the width were each increased by 3 metres, the area of the
court would be 80 m$^{2}$. Find the dimensions of the court.

{\aufgabe} Solve the following quadratic equations:
\begin{equation}
  \label{eq:chapheik}
x^{2}-4x-21=0
\end{equation}
\begin{equation}
  \label{eq:viephiru}
x^{2}-x+11=0
\end{equation}
\begin{equation}
  \label{eq:yamaghon}
x^{2}-\sqrt{5}x+1=0
\end{equation}

{\aufgabe} You have a 15\% and a 35\% solution. You mix them together
for 300 litres of a 20\% solution. How much of each original solution
did you use?

{\aufgabe} The surface of a rectangular prism is 1300cm$^{2}$. The
lengths of the sides have the ratio $4:3:2$. Calculate the volume of
the prism.

\end{document}

