% ft-lab-04.tex

\documentclass[11pt]{article}
\usepackage{enumerate}
\usepackage{syllogism} 
\usepackage{october}
\usepackage[table]{xcolor}

\newcounter{aufg}
\setcounter{aufg}{0}
\newcommand{\aufgabe}[0]{\refstepcounter{aufg}\textbf{(\arabic{aufg})}}

\begin{document}

\textbf{Exponential Equations}

{\aufgabe} Solve the equation.

  \begin{equation}
    \label{eq:phahmobu}
    8=4^{x^{2}}\cdot{}2^{5x}
  \end{equation}

{\aufgabe} Solve the equation.

  \begin{equation}
    \label{eq:poikeeng}
    2^{\frac{2}{\log_{5}x}}=\frac{1}{16}
  \end{equation}

  {\aufgabe} Solve the equation.

    \begin{equation}
    \label{eq:ohquaiva}
    2^{x^{3}}=3^{x^{2}}
  \end{equation}

{\aufgabe} John will require \$3,000 in 6 months to pay off a loan
that has no prepayment privileges. If he has the \$3,000 now, how
much of it should he save in an account paying 3\% compounded
monthly so that in six months he will have exactly \$3,000?

{\aufgabe} Priya has \$5500 and wants to invest it so that she has
\$8000 after 10 years. If compounding happens semi-annually, what
interest rate or ROI (return on investment) is she looking for?

{\aufgabe} The hotel Bora-Bora is having a pig roast. At noon, the chef put the
pig in a large earthen oven. The pig's original temperature was
$75^{\circ}F$. At 2:00\textsc{pm} the chef checked the pig's
temperature and was upset because it had reached only $100^{\circ}F$.
\begin{enumerate}
\item If the oven's temperature remains a constant $325^{\circ}F$, at
  what time may the hotel serve its guests, assuming that pork is done
  when it reaches $175^{\circ}F$?
\end{enumerate}

{\aufgabe} A small lake is stocked with a certain species of fish. The fish
  population is modeled by the function
  \begin{equation}
    \label{eq:peongeex}
    P=\frac{10}{1+4e^{-0.8t}}
  \end{equation}
where $P$ is the number of fish in thousands and $t$ is measured in
years since the lake was stocked.
\begin{enumerate}
\item Find the fish population after 3 years.
\item After how many years will the fish population reach 5000 fish?
\end{enumerate}

{\aufgabe} A culture starts with 8600 bacteria. After one hour the
  count is $10,000$.
\begin{enumerate}
\item Find a function that models the number of bacteria $n(t)$ after $t$ hours.
\item Find the number of bacteria after 2 hours.
\item After how many hours will the number of bacteria double?
\end{enumerate}

{\aufgabe} Atmospheric pressure decreases exponentially as you go higher
above sea level. It decreases about 12\% for every 1000 metres. The
pressure at sea level is 1013 hectopascal (hPa). The formula is
\begin{equation}
  \label{eq:oopohtee}
  y(t)=y(0)\cdot{}e^{ks}
\end{equation}
where $s$ is the distance above sea level in metres and $k$ is a
positive constant. What is your prediction for the air pressure on
Mount Everest (8848 metres above sea level)?

{\aufgabe} The number of people living in a country is increasing each year
exponentially. The number of people 5 years ago was 4 million. The
number of people in five years is projected to be 6.25 million. What
is the present population of the country?

\end{document}

