% ft-termtest-A-instructions.tex

\documentclass[11pt]{article}
\usepackage{enumerate}
\usepackage{syllogism} 
\usepackage{october}
\usepackage[table]{xcolor}

\newcounter{aufg}
\setcounter{aufg}{0}
\newcommand{\aufgabe}[0]{\refstepcounter{aufg}\textbf{(\arabic{aufg})}}

\begin{document}

\textbf{Term Test A Instructions}

Some rules for the term test:
\begin{itemize}
\item I will probably reseat you in random order.
\item You are only allowed to leave the classroom (for example, to go
  to the bathroom) if no one else has left the classroom. Ask for
  permission to leave. 
\item You are not allowed to submit your test to the instructor and
  leave the classroom for the first 45 minutes.
\item All electronic devices must be turned off except for a
  basic calculator.
\item If you commit an act of academic dishonesty, I will take your
  case to the dean.
\item You are graded on the steps that lead to your results. Correct
  results with incorrect or missing work to get to the results do not
  earn points.
\end{itemize}

Here is the material covered for term test A:
\begin{description}
\item[Set Theory] complements, unions, intersections, cardinality,
  subsets, disjointed sets, ordered pairs, functions, set products,
  domain, range, injective, surjective, bijective, power sets,
  interval notation, Venn diagrams.
\item[Linear Equations] solve linear equations, word problems.
\item[Quadratic Equations] complete the square, solve quadratic
  equations, word problems.
\item[Percent and Mixtures] solve word problems.
\end{description}

\end{document}

