% ft-termtest-B2.tex

\documentclass[11pt]{article}
\usepackage{alltt}
\usepackage{enumerate}
\usepackage{syllogism} 
\usepackage{october}
\usepackage[table]{xcolor}
\pagestyle{empty}

\newcounter{aufg}
\setcounter{aufg}{0}
\newcommand{\aufgabe}[1]{\refstepcounter{aufg}\textbf{(\arabic{aufg})} [#1 points]}

\begin{document}

\textbf{Term Test B version 2}

\aufgabe{5} How long will it take the world population to double at an
exponential growth rate of 1.93\% per year?

\aufgabe{5} Evaluate\begin{equation}
\log_{4}\left(2\cdot\sqrt{32}\right)+\log_{27}\sqrt{3}\notag
\end{equation}

\aufgabe{5} Solve the following equation,\begin{equation}
\ln{}2x-\ln{}4+\ln(x-2)=1\notag
\end{equation}

\aufgabe{5} Suppose that you plan to need \$10,000 in thirty-six months' time when your child starts attending university. You want to invest in an instrument yielding 3.5\% interest, compounded monthly. How much should you invest? Use the formula
\begin{equation}
A=P\left(1+\frac{r}{m}\right)^{mt}\notag
\end{equation}

\aufgabe{5} Rewrite the expression as a single logarithm,
\begin{equation}\frac{1}{3}\log(2x+1)+\frac{1}{2}[\log(x-4)-\log(x^{4}-x^{2}-1)]\notag
\end{equation}

\aufgabe{5} Suppose we are preparing a lovely \emph{Canard {\`a} l'Orange} (roast duck with orange sauce). We first take our duck out of a 32$^{\circ}$F refrigerator and place it in a 375$^{\circ}$F oven to roast. After 12 minutes the internal temperature is 57$^{\circ}$F. If we want to roast the duck until just under well-done (about 170$^{\circ}$F internally), when will it be ready?

\aufgabe{5} Evaluate without a calculator. Show all of your work.
\begin{equation}\log_{4}\left(2\cdot\sqrt{32}\right)+\log_{27}\sqrt{3}\notag
\end{equation}

\aufgabe{5} Rewrite so that there is no logarithm of a product, quotient, root, or power,
\begin{equation}\ln\frac{10^{x}}{x(x^{2}+1)(x^{4}+2)}\notag
\end{equation}

\end{document}
